Article title

### 2017-07-31 paper-webserver.tex
ADD: wording fixes

% traditional reference lab techniques
To begin analyzing genomes, researchers designate particular strains of bacterial isolates using identifiers known as subtypes.
Traditional reference laboratory techniques handled subtyping through methods such as serotyping, pulsed-field gel electrophoresis (PFGE), or Sanger sequencing, amongst others \cite{ronholm2016navigating}.
PFGE is unique amongst the set; restriction enzymes are used to produce DNA fragments visible as specific banding patterns.
Public health agencies use PFGE to track outbreaks by comparing band patterns of isolates \cite{kozak2013foodborne}.
However, as WGS rarely produces complete circular genomes and, in PFGE, cutting by a restriction enzyme is dependent on protein structure, there is no bioinformatic-analog to PFGE.
Unlike PFGE, both serotyping and MLST have WGS-based computational methods which mimick results of the wet-lab techniques.
Serotyping uses antibodies to detect the presence of specific cell surface antigens and multi-locus sequence typing (MLST), using Sanger sequencing, examines differences in housekeeping genes which are required to maintain cell function.
By comparing a pre-collected set of reference VF gene sequences against a WGS result, we can predict wet-lab serotyping results \cite{whiteside2016superphy}, Virulence Factor (VF) results \cite{joensen2014real}, and antimicrobial resistance (AMR) results \cite{mcarthur2013comprehensive}.

@@

% why Superphy
To make bioinformatic approaches user-friendly for front-line clinicians and laboratories, a variety of web services have been developed in Denmark \cite{joensen2014real}, Taiwan \cite{liu2016construction}, and in collaborations \cite{hasman2015detection}.
While useful, arguably \cite{fricke2014bacterial}, the lack of bioinformatic standards and common infrastructure technologies make it difficult to fully leverage the big-data results from WGS.
Existing software also lack ways to integrate results from multiple genomes, and examine the connections between them.

>>>>

% traditional reference lab techniques
To begin analyzing genomes, researchers designate particular strains of bacterial isolates using identifiers known as subtypes.
Traditional reference laboratory techniques handled subtyping through methods such as serotyping, pulsed-field gel electrophoresis (PFGE), or Sanger sequencing, amongst others \cite{ronholm2016navigating}.
PFGE is unique amongst the set; restriction enzymes are used to produce DNA fragments visible as specific banding patterns.
Public health agencies use PFGE to track outbreaks by comparing band patterns of isolates \cite{kozak2013foodborne}.
However, as WGS rarely produces complete circular genomes and, in PFGE, cutting by a restriction enzyme is dependent on protein structure, bioinformatic-analogs to PFGE are difficult to develop.
Unlike PFGE, both serotyping and MLST have WGS-based computational methods which mimick results of the wet-lab techniques.
Serotyping uses antibodies to detect the presence of specific cell surface antigens and multi-locus sequence typing (MLST), using Sanger sequencing, examines differences in housekeeping genes which are required to maintain cell function.
By comparing a pre-collected set of reference gene sequences against a WGS result, we can predict wet-lab serotyping results \cite{whiteside2016superphy}, Virulence Factor (VF) results \cite{joensen2014real}, and antimicrobial resistance (AMR) results \cite{mcarthur2013comprehensive}.
A similar approach can be taken for MLST \cite{larsen2012multilocus}.

@@

% why Superphy
To make bioinformatic approaches user-friendly for front-line clinicians and laboratories, a variety of web services have been developed in Denmark \cite{joensen2014real,larsen2012multilocus}, Taiwan \cite{liu2016construction}, and in collaborations \cite{hasman2015detection}.
While useful, arguably \cite{fricke2014bacterial}, the lack of bioinformatic standards and common infrastructure technologies make it difficult to fully leverage the big-data results from WGS.
Existing software also lack ways to integrate results from multiple genomes, and examine the connections between them.
